---
title: "R_assignment0924_practice2.2"
author: "he-ping"
date: "2024-09-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practice 2.2 

#Using the iris dataset create a new variable with flower colors. 
#Iris setosa is purple.Iris versicolor is blue. Iris virginica is pink. 
#Sort individuals by decreasing Sepal.Width. 
#What can you hypothesize on the size of sepal for these three species. 
#Get back the data set for the species having the smallest sepal width. 
#Delete the variable color in this subset*

# read data
```{r }
#read data
library(datasets)
data(iris)
iris
```

# Iris setosa is purple.Iris versicolor is blue. Iris virginica is pink.
```{r }
#Iris setosa is purple.Iris versicolor is blue. Iris virginica is pink.
color <- ifelse(iris$Species == "setosa", 'purple',ifelse(iris$Species == "versicolor", 'blue', 'pink'))
color
iris$colors <- ifelse(iris$Species == "setosa", 'purple',ifelse(iris$Species == "versicolor", 'blue', 'pink'))
iris
```

# What can you hypothesize on the size of sepal for these three species.
```{r }
#What can you hypothesize on the size of sepal for these three species.
#setosa
setosa <- iris$Species == "setosa"
iris_setosa <- iris[setosa, ]
iris_setosa
mean_se_len <- mean(iris_setosa$Sepal.Length)
mean_se_width <- mean(iris_setosa$Sepal.Width)
mean_se_len
mean_se_width

```

```{r }
#versicolor
versicolor <- iris$Species == "versicolor"
iris_versicolor <- iris[versicolor, ]
iris_versicolor
mean_ve_len <- mean(iris_versicolor$Sepal.Length)
mean_ve_width <- mean(iris_versicolor$Sepal.Width)
mean_ve_len
mean_ve_width
```

```{r }
#virginica
virginica <- iris$Species == "virginica"
iris_virginica <- iris[virginica, ]
iris_virginica
mean_vi_len <- mean(iris_virginica$Sepal.Length)
mean_vi_width <- mean(iris_virginica$Sepal.Width)
mean_vi_len
mean_vi_width
```

# Get back the data set for the species having the smallest sepal width.
```{r }
#Get back the data set for the species having the smallest sepal width.
mean_se_width
mean_ve_width
mean_vi_width
```

```{r }
versicolor <- iris$Species == "versicolor"
iris_versicolor <- iris[versicolor, ]
iris_versicolor
mean_ve_width
```

# Delete the variable color in this subset*
```{r }
#Delete the variable color in this subset*
iris_versicolor$colors<-NULL
iris_versicolor
```
