---
title: "1022_assignment"
author: "he-ping"
date: "2024-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practice 4.2

Using the rairuoho dataset you will use a ggplot2 visualization to show that over the course of the experiment the growth of the grass is becoming higher in the nutrient treatment than in the water treatment. You are free to use the visualization that you think makes the most sense Do not forget to embellish your visualization and the use of a legend and/or theme.

# Read rairuoho dataset
```{r }
# read rairuoho dataset 
url <- "https://www.dipintothereef.com/uploads/3/7/3/5/37359245/rairuoho.txt"
data <- read.csv(url, header = TRUE, sep = "\t")
data
```

# Install pakage
```{r }
# install pakage
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
```

# Choice the data
```{r }
# choice the data
data_select1 <- data %>%
  select(-spatial1, -spatial2, -row, -column) %>% #remove
  mutate(growth = day8 - day3) #caculate growth

data_select2 <- data_select1 %>%
  select(-day3, -day4, -day5, -day6, -day7, -day8) %>% #remove
  arrange(desc(treatment == "water"), growth) #group
data_select2
```

# Print ggplot
```{r }
# ggplot
p <- ggplot(data_select2, aes(x = treatment, y = growth, fill = treatment)) +
  geom_boxplot(alpha = 0.7, width = 0.5, outlier.size = 1.5, outlier.shape = 16) + 
  geom_jitter(width = 0.15, size = 1.0, color = "black", shape = 16) +  
  labs(
    title = "Grass Growth under Nutrient and Water Treatments",
    x = "Treatment Type",
    y = "Grass Growth (cm)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.31, size = 10),  
    axis.title = element_text(face = "bold", size = 10),               
    axis.text = element_text(size = 9, color = "black"),              
    panel.grid.major = element_blank(),                               
    panel.grid.minor = element_blank(),                                
    panel.border = element_rect(color = "black", fill = NA, size = 1),  
    legend.text = element_text(size = 10, color = "black"),           
    legend.title = element_text(face = "bold", size = 10, color = "black")
  ) +
  scale_fill_manual(values = c("nutrient" = "#2a9d8f", "water" = "#e76f51"))
p
```

#  Statistical analysis
```{r }
#  ANOVA
anova_results <- aov(growth ~ treatment, data = data_select2)
summary(anova_results)
```

```{r }
# TukeyHSD
posthoc_results <- TukeyHSD(anova_results)
print(posthoc_results)
```

# Add statistical results
```{r }
# statistical results
p + 
  geom_segment(aes(x = 1, xend = 2, y = max(data_select2$growth) + 5, yend = max(data_select2$growth) + 5),
               color = "black", size = 0.6) +  # line
  geom_text(aes(x = 1.5, y = max(data_select2$growth) + 6, 
                label = "***"), size = 4, color = "black")  # annotation
```

# Saving plot 
```{r, eval = FALSE}
ggsave("grass_growth_analysis.pdf", plot = last_plot(), 
       width = 9, height = 7, units = "cm", dpi = 300)
```